---
title: "Basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(compr)
```

The purpose of the `compr` package is to provide functionality for fitting paired competition models in `R`. The primary function, `comp_glm()` has the following arguments:

* `formula`, giving the response variable (a numeric vector of 0's and 1's) and contest-level predictors.
* `data`, the data used.
* `p1`, a string with the name of the column with the first player. 
* `p2`, a string with the name of the column with the second player.
* `p1_effects`, a one-sided formula with player-level effects for `p1`
* `p2_effects`, a one-sided formula with player-level effects for `p2`.
* `ref_player`, a string giving the name of the player to be used as the reference player (taken to be the first player in `p1` by default).


```{r}
comp_mod <- comp_glm(point_winner ~ -1, data = tennis_point,
                     p1 = "player1", p2 = "player2",
                     p1_effects = ~ point_server1,
                     p2_effects = ~ point_server2,
                     ref_player = "Milos Raonic")
```

The `comp_mod` object is of class `glm` so any generic summary functions for basic `glm()` models can also be applied to models fit with `comp_glm()`:

```{r}
summary(comp_mod)
AIC(comp_mod)

library(broom)
tidy(comp_mod)
glance(comp_mod)

augment(comp_mod) ## need to clean up names
augment(comp_mod) |> names()
```
